\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{xcolor}

\begin{document}

\title{SH-DFS: An Explainable Self-Healing Machine Learning Pipeline for Product Demand Forecasting}

\author{\IEEEauthorblockN{Your Name}
\IEEEauthorblockA{\textit{Department of Computer Science} \\
\textit{Your University}\\
City, Country \\
email@university.edu}
\and
\IEEEauthorblockN{Co-author Name}
\IEEEauthorblockA{\textit{Department of Engineering} \\
\textit{Your University}\\
City, Country \\
email@university.edu}}

\maketitle

\begin{abstract}
Deployed machine learning models for demand forecasting degrade over time as real-world data distributions shift — a phenomenon known as data drift. This paper presents SH-DFS (Self-Healing Demand Forecasting System), a production-ready platform that combines dynamic feature engineering, multi-method drift detection, autonomous self-healing, and a sequential monthly prediction cycle. The system accepts any CSV with Date, Product, and Demand columns and auto-generates 40--87+ engineered features spanning temporal patterns, lag windows, rolling statistics, product statistics, store statistics, and pairwise interactions. An ensemble of Random Forest, Gradient Boosting, and XGBoost models is trained with TimeSeriesSplit cross-validation; the best performer is selected automatically. During a 12-month test simulation, five complementary drift detection methods (Kolmogorov-Smirnov, Population Stability Index, Wasserstein distance, Jensen-Shannon divergence, and error trend analysis) evaluate each month, and a fine-tuner applies targeted model updates with automatic rollback if performance does not improve. After training, the system enters a continuous monthly prediction cycle: it predicts the next month, accepts uploaded actuals, compares predictions against reality, and repeats indefinitely. Evaluated on the Kaggle Store Item Demand Forecasting dataset (52,500 weekly rows, 10 stores, 50 products, 2 years), the system achieves R$^{2}$ = 0.9999 and MAPE $<$ 1\% on training data, successfully detects drift across all 12 test months, and serves results through a FastAPI backend and a 10-page React dashboard with real-time polling.
\end{abstract}

\begin{IEEEkeywords}
Demand Forecasting, Self-Healing ML, Drift Detection, Feature Engineering, Explainable AI, Sequential Prediction
\end{IEEEkeywords}

\section{Introduction}

Accurate product demand forecasting is essential for inventory management, supply chain planning, and retail operations. Machine learning models trained on historical data face a fundamental challenge in production: the statistical properties of incoming data change over time, causing model performance to degrade silently. Traditional monitoring systems detect this degradation but require manual intervention to retrain or adjust models — a costly and slow process.

This paper presents SH-DFS, a complete self-healing demand forecasting platform designed for production deployment. The system is built around three core ideas: (1) dynamic feature engineering that works with any dataset containing Date, Product, and Demand; (2) multi-method drift detection with importance-weighted thresholds; and (3) a continuous monthly prediction cycle that closes the loop between predictions and actuals.

Unlike prior work that proposes LLM-based diagnosis \cite{rauba2024self} or fixed action catalogs, SH-DFS implements practical, cost-free healing through targeted fine-tuning with automatic rollback. The system is fully deployed as a FastAPI backend and React frontend, making it immediately usable without additional infrastructure.

Our key contributions are:

\begin{enumerate}
    \item \textbf{Dynamic Feature Engineering:} Auto-generates 40--87+ features from any Date+Product+Demand dataset, including temporal cycles, lag windows (1--52 weeks), rolling statistics (4--26 week windows), product and store statistics, and dynamic pairwise interactions between any numeric columns present.

    \item \textbf{8-Step ML Pipeline:} Load $\rightarrow$ Split $\rightarrow$ Feature Engineering $\rightarrow$ Train $\rightarrow$ Simulate Months $\rightarrow$ Summary $\rightarrow$ Save $\rightarrow$ First Prediction. Each step is logged and recoverable.

    \item \textbf{Multi-Method Drift Detection:} Five statistical methods with feature-importance-weighted thresholds, aggregated into a single severity classification (none / mild / severe) per month.

    \item \textbf{Self-Healing with Rollback:} Fine-tuner applies model updates when drift is detected; automatically rolls back if the updated model does not improve MAE by at least 5\%.

    \item \textbf{Sequential Monthly Prediction Cycle:} After training, the system predicts Month N+1, accepts uploaded actuals for Month N, compares predictions vs reality, and auto-predicts Month N+2 — repeating indefinitely.

    \item \textbf{Production-Ready Implementation:} FastAPI backend with 30+ endpoints, in-memory caching with TTL, GZip compression, CORS security, and a 10-page React dashboard with real-time polling and skeleton loading.
\end{enumerate}

\section{Related Work}

\subsection{Data Drift Detection}

Gama et al.\ \cite{gama2014survey} survey concept drift detection methods, covering statistical tests and adaptive learning. Classical approaches include the Kolmogorov-Smirnov test for distribution comparison and Population Stability Index (PSI) for magnitude measurement. Wasserstein distance \cite{villani2009optimal} and Jensen-Shannon divergence provide complementary perspectives on distribution shift. Our system combines all five methods to reduce false positives and missed detections.

\subsection{Demand Forecasting with Machine Learning}

Makridakis et al.\ \cite{makridakis2018statistical} compare classical and ML forecasting methods. Tree-based ensembles (Random Forest \cite{breiman2001random}, Gradient Boosting \cite{friedman2001greedy}, XGBoost \cite{chen2016xgboost}) consistently outperform classical methods on retail demand data when combined with rich feature engineering. Our system automates this feature engineering pipeline and selects the best model automatically.

\subsection{Self-Healing Machine Learning}

Rauba et al.\ \cite{rauba2024self} introduced Self-Healing Machine Learning (SHML), proposing LLM-based diagnosis for autonomous adaptation. While theoretically powerful, LLM-based approaches introduce latency (20--40 seconds per cycle), ongoing API costs, and external dependencies. SH-DFS achieves self-healing through direct statistical fine-tuning with no external dependencies.

\section{System Architecture}

\subsection{Overview}

SH-DFS consists of two independent services: a Python FastAPI backend and a React frontend. The backend runs an 8-step pipeline on uploaded data, stores results in JSON logs and CSV files, and serves them through a REST API. The frontend polls the API and renders 10 dashboard pages.

\subsection{Data Requirements}

The system accepts any CSV file with three required columns:

\begin{itemize}
    \item \textbf{Date} (DD-MM-YYYY): Week date
    \item \textbf{Product} (integer): Product identifier
    \item \textbf{Demand} (integer): Units demanded
\end{itemize}

Optional columns are auto-detected: Store, Holiday\_Flag, Temperature, Fuel\_Price, CPI, Unemployment, or any other numeric/text columns. Common aliases are auto-renamed (e.g., \texttt{sales}$\rightarrow$Demand, \texttt{item}$\rightarrow$Product).

\subsection{8-Step Pipeline}

\begin{enumerate}
    \item \textbf{Load \& Inspect:} Read CSV, validate required columns, detect optional columns, compute data inspection statistics.
    \item \textbf{Split:} Year 1 $\rightarrow$ Training, Year 2 $\rightarrow$ Testing (chronological split by calendar year).
    \item \textbf{Feature Engineering:} Generate 40--87+ features; save engineer state for future predictions.
    \item \textbf{Train Model:} RandomizedSearchCV with TimeSeriesSplit; train RF, GB, XGB; select best by MAE; compute 95\% confidence intervals.
    \item \textbf{Simulate Months:} For each test month: predict $\rightarrow$ detect drift $\rightarrow$ apply healing action $\rightarrow$ log results.
    \item \textbf{Generate Summary:} Aggregate severity counts, healing statistics, average improvement.
    \item \textbf{Save Results:} Write phase1\_summary.json, drift\_history.json, healing\_history.json, processed/predictions\_*.csv.
    \item \textbf{First Prediction:} Predict the first future month using the trained model and sequential predictor.
\end{enumerate}

\section{Dynamic Feature Engineering}

The feature engineering pipeline in \texttt{feature\_engineering.py} auto-detects available columns and generates features in seven groups:

\subsection{Temporal Features (18)}

Year, Month, Week, Quarter, DayOfYear, Is\_Year\_End, Is\_Year\_Start, Is\_Q4, cyclical encodings (Week\_Sin, Week\_Cos, Month\_Sin, Month\_Cos), proximity to three universal holiday windows (weeks 6, 47, 51), Near\_Holiday flag, and Season (label-encoded: Winter/Spring/Summer/Fall).

\subsection{Lag Features (9)}

Lag\_1 through Lag\_52 (at offsets 1, 2, 3, 4, 8, 12, 26, 52 weeks) computed per Product (and Store if present) using grouped shift. Missing values are filled with group means. Lag\_52\_ratio = Lag\_52 / (Lag\_1 + 1) captures year-over-year momentum.

\subsection{Rolling Statistics (16)}

For windows of 4, 8, 12, and 26 weeks: Rolling\_Mean, Rolling\_Std, Rolling\_Max, Rolling\_Min — all computed on shifted demand (shift(1)) to prevent data leakage.

\subsection{Momentum and Volatility (4)}

Momentum\_4 = Lag\_1 / (Rolling\_Mean\_4 + 1), Momentum\_12 = Lag\_1 / (Rolling\_Mean\_12 + 1), Volatility\_4 = Rolling\_Std\_4 / (Rolling\_Mean\_4 + 1), Volatility\_12 = Rolling\_Std\_12 / (Rolling\_Mean\_12 + 1).

\subsection{Product Statistics (8)}

If Product column exists: Product\_Mean, Product\_Median, Product\_Std, Product\_Max, Product\_Min (computed on training data, applied to test), plus Demand\_vs\_Product\_Mean, Demand\_vs\_Product\_Median, Product\_CV.

\subsection{Store Statistics (8)}

If Store column exists: Store\_Mean, Store\_Median, Store\_Std, Store\_Max, Store\_Min, Demand\_vs\_Store\_Mean, Demand\_vs\_Store\_Median, Store\_CV.

\subsection{Interaction Features (up to 19)}

Known interactions: Store$\times$Holiday, Product$\times$Holiday, Store$\times$Product, Temperature$\times$Fuel\_Price, CPI$\times$Unemployment, Unemployment/CPI, Fuel$\times$Unemployment, CPI$\times$Fuel, Temperature$\times$Holiday, Holiday$\times$Q4 — created only when both columns exist. Dynamic pairwise: up to 10 additional products of any two user-provided numeric columns.

\subsection{Feature Count by Input}

\begin{table}[htbp]
\caption{Features Generated by Input Columns}
\centering
\begin{tabular}{|l|c|}
\hline
\textbf{Input Columns} & \textbf{Features} \\
\hline
Date + Product + Demand & $\sim$48 \\
+ Store & $\sim$56 \\
+ Store + 5 economic columns & $\sim$87 \\
\hline
\end{tabular}
\label{tab:features}
\end{table}

\section{Model Training}

\subsection{Hyperparameter Tuning}

RandomizedSearchCV with TimeSeriesSplit (n\_splits = min(5, max(2, $\lfloor$rows/50$\rfloor$))) searches over:

\begin{itemize}
    \item n\_estimators: [200, 300, 500]
    \item max\_depth: [None, 20, 30]
    \item min\_samples\_split: [2, 5]
    \item min\_samples\_leaf: [1, 2]
    \item max\_features: ['sqrt', 0.5, 0.7]
\end{itemize}

\subsection{Ensemble Selection}

Three models are trained: Random Forest (tuned), Gradient Boosting (n\_estimators=300, max\_depth=5, lr=0.03), and XGBoost (n\_estimators=300, max\_depth=6, lr=0.03). For datasets $\geq$ 100 rows with XGBoost available, a StackingRegressor combines all three with a Ridge meta-learner. The best model by MAE is saved as \texttt{active\_model.pkl}.

\subsection{Confidence Intervals}

95\% prediction intervals are computed from Random Forest tree variance:

\begin{equation}
\text{CI} = \bar{y} \pm 1.96 \cdot \sigma_{\text{trees}}
\end{equation}

where $\bar{y}$ is the mean prediction across all trees and $\sigma_{\text{trees}}$ is their standard deviation.

\section{Drift Detection}

\subsection{Five Detection Methods}

\textbf{Kolmogorov-Smirnov Test:}
\begin{equation}
D_{n,m} = \sup_x |F_{1,n}(x) - F_{2,m}(x)|
\end{equation}
Thresholds: $D < 0.05$ (none), $0.05$--$0.15$ (mild), $> 0.2$ (severe).

\textbf{Population Stability Index:}
\begin{equation}
\text{PSI} = \sum_{i=1}^{10} (A_i\% - E_i\%) \cdot \ln\!\left(\frac{A_i\%}{E_i\%}\right)
\end{equation}
Thresholds: $< 0.1$ (none), $0.1$--$0.25$ (mild), $> 0.25$ (severe).

\textbf{Wasserstein Distance:} Earth mover's distance computed on the top 10 features by importance.

\textbf{Jensen-Shannon Divergence:}
\begin{equation}
\text{JSD}(P\|Q) = \tfrac{1}{2}\text{KL}(P\|M) + \tfrac{1}{2}\text{KL}(Q\|M), \quad M = \tfrac{1}{2}(P+Q)
\end{equation}

\textbf{Error Trend Analysis:}
\begin{equation}
\text{Error Increase} = \frac{\text{MAE}_{\text{current}} - \text{MAE}_{\text{baseline}}}{\text{MAE}_{\text{baseline}}} \times 100
\end{equation}
Increase $> 10\%$ triggers a drift alert.

\subsection{Feature-Importance-Weighted Thresholds}

Feature importances from the trained model's \texttt{feature\_importances\_} attribute are used to adjust detection thresholds:

\begin{itemize}
    \item Top 20\% importance: thresholds $\times$ 0.7 (more sensitive)
    \item Bottom 20\% importance: thresholds $\times$ 1.3 (less sensitive)
    \item Middle 60\%: baseline thresholds
\end{itemize}

\subsection{Severity Aggregation}

Each month receives a single severity label:
\begin{itemize}
    \item \textbf{Severe:} Any feature with KS $> 0.2$ or PSI $> 0.25$, OR error increase $> 10\%$
    \item \textbf{Mild:} $> 30\%$ of features show mild drift
    \item \textbf{None:} Otherwise
\end{itemize}

\section{Self-Healing}

\subsection{Healing Actions}

For each simulated test month, the fine-tuner in \texttt{fine\_tuner.py} decides:

\begin{itemize}
    \item \textbf{Monitor:} Severity = none. No model change.
    \item \textbf{Fine-Tune:} Severity = mild or severe. Add estimators to the ensemble using the current month's data as additional training signal.
    \item \textbf{Rollback:} If fine-tuning does not improve MAE by $\geq 5\%$, revert to the previous model version.
\end{itemize}

\subsection{Model Versioning}

Each fine-tuned model is saved as \texttt{model\_v1\_\{timestamp\}.pkl} with a corresponding metadata JSON. The active model is always \texttt{active\_model.pkl}. Rollback restores the previous version atomically.

\section{Sequential Monthly Prediction Cycle}

After the 8-step pipeline completes, the system enters a continuous prediction cycle managed by \texttt{sequential\_predictor.py}:

\begin{enumerate}
    \item \textbf{Predict Next Month:} Build scaffold rows (one per Product per week), fill optional columns with last-known values, run feature engineering on combined historical + scaffold data, predict Demand for each row.
    \item \textbf{Upload Actuals:} User uploads a CSV with Date + Product + Demand for the completed month.
    \item \textbf{Compare:} System computes MAE, MAPE, RMSE between predictions and actuals; saves comparison to \texttt{logs/comparison\_\{month\}.json}.
    \item \textbf{Auto-Predict:} System immediately predicts the next month and saves results to \texttt{predictions/\{month\}\_predictions.csv}.
    \item \textbf{Repeat:} Cycle continues indefinitely.
\end{enumerate}

\subsection{Auto-Fill for Future Months}

When predicting a future month, optional columns (Temperature, CPI, etc.) are not yet available. The system fills them with the last known values from the most recent historical row, ensuring feature engineering can still compute all 40--87+ features using real lag and rolling values from historical demand.

\section{API and Dashboard}

\subsection{REST API}

The FastAPI backend exposes 30+ endpoints with in-memory caching (TTL 30--600 seconds per endpoint), GZip compression, and stale-while-revalidate HTTP headers.

\begin{table}[htbp]
\caption{Core API Endpoints}
\centering
\renewcommand{\arraystretch}{1.1}
\begin{tabular}{|l|l|}
\hline
\textbf{Endpoint} & \textbf{Purpose} \\
\hline
GET /api/health & System health + model status \\
GET /api/summary & Phase 1 summary + healing stats \\
GET /api/drift & Drift history (deduped by month) \\
GET /api/feature-importances & Model feature importances \\
GET /api/predictions/\{month\} & Test set predictions for a month \\
GET /api/predictions-meta & File mtimes for change detection \\
GET /api/processed-months & Available test months \\
GET /api/product-demand & Per-product total demand \\
GET /api/product-forecast & Per-product accuracy summary \\
GET /api/product-monthly & Monthly demand per product \\
GET /api/demand-metrics & Avg demand, growth rate, peak month \\
GET /api/monthly-demand & Monthly aggregated demand \\
GET /api/monthly-sales & Actual vs predicted per month \\
GET /api/store-stats & Per-store MAE aggregation \\
POST /api/upload-predict & Upload CSV $\rightarrow$ run pipeline (async) \\
GET /api/seq/status & Sequential predictor state \\
POST /api/seq/predict-next & Predict next month \\
POST /api/seq/upload-actuals & Upload actuals $\rightarrow$ compare $\rightarrow$ predict \\
GET /api/seq/prediction/\{month\} & Saved sequential prediction \\
GET /api/seq/comparison/\{month\} & Predicted vs actual comparison \\
\hline
\end{tabular}
\label{tab:api}
\end{table}

The \texttt{/api/upload-predict} endpoint runs the pipeline in a thread executor with a 600-second timeout, returning HTTP 504 on timeout. The \texttt{/api/seq/upload-actuals} endpoint sanitizes NaN/Inf values recursively before JSON serialization.

\subsection{React Dashboard}

The frontend is built with React 18 + Vite, using Recharts for all charts. All pages are lazy-loaded; slow API endpoints are pre-warmed on idle startup via \texttt{requestIdleCallback}. The \texttt{useFetch} hook implements dedup fetch, in-memory caching (60-second TTL), stale-while-revalidate, and configurable polling intervals.

The dashboard has 10 pages organized in three groups:

\textbf{Baseline vs Test Set:}
\begin{enumerate}
    \item \textbf{Training Overview:} R², MAE, RMSE, MAPE KPIs; MAE trend bar; drifted features per month; monthly test set vs predicted area chart; healing action summary.
    \item \textbf{Drift Detection:} Error increase bar (color-coded by severity); drifted feature count stacked bar; full drift history table with KS/PSI/Wasserstein values.
    \item \textbf{Baseline Performance:} MAE/RMSE/MAPE/R² KPIs; MAE trend with brush; error increase line with threshold reference; metrics glossary.
\end{enumerate}

\textbf{Analysis:}
\begin{enumerate}
    \setcounter{enumi}{3}
    \item \textbf{Feature Importance:} Top-20 horizontal bar; feature group treemap; group filter pills; radial chart; per-group feature cards.
    \item \textbf{Forecasting (StoreStats):} Monthly forecast vs test set area+line; accuracy by product bar; MAE by product; radar chart; product detail table.
    \item \textbf{Predictions Explorer:} Test set vs predicted with 95\% CI band + brush; product demand summary bar; monthly avg area; absolute error bar; 100-row detail table with quality badges.
    \item \textbf{Demand Insights:} Avg weekly demand, growth rate, peak month KPIs; demand vs forecast bar; demand share pie (no legend); monthly aggregation bar; normalized radar; product$\times$month heatmap.
\end{enumerate}

\textbf{Data:}
\begin{enumerate}
    \setcounter{enumi}{7}
    \item \textbf{Datasets:} Train/test split info; drift severity summary; monitored batches table.
    \item \textbf{Upload \& Monitor:} Drag-and-drop CSV upload; async pipeline progress; healing status; post-pipeline KPIs and charts.
    \item \textbf{Predict Cycle:} Sequential prediction workflow; upload actuals; comparison charts; accuracy history; saved predictions browser.
\end{enumerate}

\section{Experimental Results}

\subsection{Dataset}

Kaggle Store Item Demand Forecasting dataset: daily sales for 50 items across 10 stores (2013--2017). Aggregated to weekly by store+item, filtered to 2 years (2016 training, 2017 testing): 52,500 rows, 10 stores, 50 products. Columns: Date, Store, Product, Demand.

\subsection{Model Performance}

\begin{table}[htbp]
\caption{Model Performance on Training Data}
\centering
\begin{tabular}{|l|c|}
\hline
\textbf{Metric} & \textbf{Value} \\
\hline
R$^{2}$ & 0.9999 \\
MAE & $<$ 1 unit \\
MAPE & $<$ 1\% \\
Model & Gradient Boosting \\
Features & 63 \\
\hline
\end{tabular}
\label{tab:metrics}
\end{table}

\subsection{Drift Detection Results}

All 12 test months (2017) exhibited drift relative to the 2016 training baseline, as expected from the temporal gap. The system detected drift in all months using the five-method ensemble. Healing actions were applied to months with mild or severe drift; rollback was triggered when fine-tuning did not meet the 5\% improvement threshold.

\subsection{Sequential Prediction}

After the pipeline, the system predicted 2018-01 (first future month). Subsequent months (2026-02, 2026-03) were predicted after uploading actuals, demonstrating the continuous prediction cycle.

\subsection{System Performance}

\begin{itemize}
    \item Pipeline execution: 60--120 seconds for 52,500 rows
    \item API response: $<$ 50ms for cached endpoints
    \item Frontend load: $<$ 2 seconds (lazy loading + API pre-warming)
    \item Memory: $<$ 1 GB for full pipeline
\end{itemize}

\section{Discussion}

\subsection{Design Decisions}

The choice to use five complementary drift detection methods rather than a single method reduces both false positives (a single method might flag noise) and false negatives (a single method might miss subtle shifts). Feature-importance weighting further reduces false positives by relaxing thresholds for low-importance features.

The rollback mechanism is critical for production safety: fine-tuning on a single month's data can overfit, and the 5\% improvement threshold ensures the model only updates when there is a meaningful benefit.

The sequential prediction cycle closes the feedback loop that most monitoring systems leave open. Rather than just detecting drift, SH-DFS continuously produces actionable predictions and measures their accuracy against reality.

\subsection{Limitations}

\begin{enumerate}
    \item Validated on a single dataset; generalizability to other domains requires further study.
    \item Batch processing mode; not designed for real-time streaming.
    \item In-memory caching does not persist across server restarts.
    \item Fine-tuning adds estimators to the ensemble; long-running systems may accumulate large models.
\end{enumerate}

\subsection{Future Work}

\begin{enumerate}
    \item Automated retraining (full retrain, not just fine-tune) when drift persists across multiple months.
    \item SHAP-based real-time explanations for individual predictions.
    \item PostgreSQL/Redis for persistent caching and enterprise-scale storage.
    \item Streaming ingestion for real-time demand signals.
    \item Multi-objective healing: optimize for business KPIs (stockout cost, overstock cost) in addition to MAE.
\end{enumerate}

\section{Conclusion}

This paper presented SH-DFS, a production-ready self-healing demand forecasting system that integrates dynamic feature engineering (40--87+ features from any Date+Product+Demand dataset), five-method drift detection with importance-weighted thresholds, fine-tuning with automatic rollback, and a continuous monthly prediction cycle. Evaluated on 52,500 weekly rows across 10 stores and 50 products, the system achieves near-perfect training accuracy and successfully detects and responds to drift across all 12 test months. The complete implementation — FastAPI backend, 10-page React dashboard, and sequential predictor — demonstrates that effective self-healing ML can be achieved without LLM dependencies or external services, making it practical for real-world deployment.

\begin{thebibliography}{99}

\bibitem{gama2014survey} J. Gama, I. \v{Z}liobait\.{e}, A. Bifet, M. Pechenizkiy, and A. Bouchachia, ``A survey on concept drift adaptation,'' \textit{ACM Computing Surveys}, vol. 46, no. 4, pp. 1--37, 2014.

\bibitem{rauba2024self} P. Rauba, N. Seedat, K. Kacprzyk, and M. van der Schaar, ``Self-Healing Machine Learning: A Framework for Autonomous Adaptation in Real-World Environments,'' in \textit{Neural Information Processing Systems (NeurIPS)}, 2024.

\bibitem{makridakis2018statistical} S. Makridakis, E. Spiliotis, and V. Assimakopoulos, ``Statistical and machine learning forecasting methods: Concerns and ways forward,'' \textit{PLoS ONE}, vol. 13, no. 5, p. e0194889, 2018.

\bibitem{breiman2001random} L. Breiman, ``Random Forests,'' \textit{Machine Learning}, vol. 45, no. 1, pp. 5--32, 2001.

\bibitem{friedman2001greedy} J. H. Friedman, ``Greedy function approximation: A gradient boosting machine,'' \textit{Annals of Statistics}, vol. 29, no. 5, pp. 1189--1232, 2001.

\bibitem{chen2016xgboost} T. Chen and C. Guestrin, ``XGBoost: A scalable tree boosting system,'' in \textit{Proceedings of the 22nd ACM SIGKDD International Conference on Knowledge Discovery and Data Mining}, 2016, pp. 785--794.

\bibitem{villani2009optimal} C. Villani, \textit{Optimal Transport: Old and New}. Springer, 2009.

\bibitem{lundberg2017unified} S. M. Lundberg and S.-I. Lee, ``A unified approach to interpreting model predictions,'' in \textit{Advances in Neural Information Processing Systems}, 2017, pp. 4765--4774.

\end{thebibliography}

\end{document}
